### 2025-03-09 MAT185 Lecture Notes/main.tex
march 9

\end{example}
\begin{theorem}[Properties of Linear Transformation]
    Let $T: V \rightarrow W$ be a linear transformation, then:
    \begin{enumerate}
        \item $T(\textbf{0}) = \textbf{0}$
        \item $T(\textbf{x} - \textbf{y}) = T(\textbf{x}) - T(\textbf{y})$
    \end{enumerate}
\end{theorem}
\begin{proof}
    We have $T(\textbf{0} + X) = T(X) = T(\textbf{0}) + T(X)$. Thus, $T(\textbf{0}) = \textbf{0}$, by the Cancelation Theorem. We also have $T(\textbf{x} - \textbf{y}) = T(\textbf{x} + (-\textbf{y})) = T(\textbf{x}) + T(-\textbf{y}) = T(\textbf{x}) - T(\textbf{y})$.
\end{proof}
\end{document}

>>>>

\begin{theorem}[Properties of Linear Transformation]
    Let $T: V \rightarrow W$ be a linear transformation, then:
        \item $T(\textbf{0}) = \textbf{0}$
        \item $T(\textbf{x} - \textbf{y}) = T(\textbf{x}) - T(\textbf{y})$
    We have $T(\textbf{0} + X) = T(X) = T(\textbf{0}) + T(X)$. Thus, $T(\textbf{0}) = \textbf{0}$, by the Cancelation Theorem. We also have $T(\textbf{x} - \textbf{y}) = T(\textbf{x} + (-\textbf{y})) = T(\textbf{x}) + T(-\textbf{y}) = T(\textbf{x}) - T(\textbf{y})$.
\begin{definition}[Kernel and Image]
    Let $T: V \rightarrow W$ be a linear transformation, then: 
        \item The \textbf{kernel} of $T$, denoted as $\ker(T)$, is the set of all vectors in $V$ that map to the zero vector in $W$. Formally,
        \[
        \ker(T) = \{ \textbf{v} \in V \mid T(\textbf{v}) = \textbf{0} \}
        \]
        \item The \textbf{image} of $T$, denoted as $\text{Im}(T)$, is the set of all vectors in $W$ that are images of vectors in $V$. Formally,
        \[
        \text{Im}(T) = \{ T(\textbf{v}) \mid \textbf{v} \in V \}
        \]
\begin{theorem}[Rank-Nullity for LT]
    Let $T: V \rightarrow W$ be a linear transformation, then:
    \begin{equation}
        \dim(\ker(T)) + \dim(\text{Im}(T)) = \dim(V)
    \end{equation}
\begin{definition}[Injective LT]
    Let $T: V \rightarrow W$ be a linear transformation, then $T$ is injective if $x_1 \neq x_2 \implies T(x_1) \implies T(x_2)$
\begin{theorem}
    If the nullity of $T$, $\text{dim ker} T$ is greater than zero, then $T$ is not injective.
\begin{definition}[Surjective]
    Let $T: V \rightarrow W$ be a linear transformation, then $T$ is surjective if for every $y \in W$, there exist an $x \in V$ so that $T(x) = y$.
\begin{definition}[Bijective]
    Let $T: V \rightarrow W$ be a linear transformation, then $T$ is bijective if $T$ is both injective and surjective.
\begin{theorem}[Basis function is LT]
    Let $\alpha = \{\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n\}$ be a basis for vector space $V$. The function $T: V \to \mathbb{R}^n$ defined by $T(v) = [v]_\alpha$ is a linear transformation.
\subsection{Change of Basis}
\begin{definition}[Change of Basis]
    Let $\alpha = \{\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n\}$ and $\beta = \{\textbf{w}_1, \textbf{w}_2, \ldots, \textbf{w}_n\}$ be two bases for vector space $V$. The change of basis matrix $P$ is defined as:
    \begin{equation}
        P = [\textbf{w}_1, \textbf{w}_2, \ldots, \textbf{w}_n]_\alpha
    \end{equation}
\begin{theorem}[Change of Basis Matrix]
    Let $\alpha = \{\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n\}$ and $\beta = \{\textbf{w}_1, \textbf{w}_2, \ldots, \textbf{w}_n\}$ be two bases for vector space $V$. The change of basis matrix $P$ is defined as:
    \begin{equation}
        P = [\textbf{w}_1, \textbf{w}_2, \ldots, \textbf{w}_n]_\alpha
    \end{equation}
\paragraph{Stacking Chnage of Basis Matrix} We can stack the change of basis matrix to form a matrix $P$, and also incoperate linear transformations in other bases to a vector.
\section{Determinants}
\begin{definition}[Determinant]
    Let $A \in \mathbb{R}^{n \times n}$, then the determinant of $A$ is denoted as $\det(A)$.
\begin{example}
    Consider the following $2\times 2$ system:
        ax + by &= 0 \\
        cx + dy &= 0
    The the system has the general solution:
        x &= \frac{dy}{ad - bc} \\
        y &= \frac{-cx}{ad - bc}
    The denominator $ad - bc$ is the determinant of the matrix. Notice that if the determinant is zero, then the system has no unique solution.
\begin{theorem}[Propeties of $2 \times 2$ Determinant]
    Let $A = \begin{bmatrix} a & b \\ c & d \end{bmatrix}$, then:
        \det(A) &= ad - bc \\
        \det\left(\begin{bmatrix}
            br_1 + cr_1^\prime \\ r_2
        \end{bmatrix}\right) &= b\det\left(\begin{bmatrix}
            r_1 \\ r_2
        \end{bmatrix}\right) + c\det\left(\begin{bmatrix}
            r_1^\prime \\ r_2 
        \end{bmatrix}\right) \\
        \det\left(\begin{bmatrix}
            r_1 \\ r_2
        \end{bmatrix}\right) &= -\det\left(\begin{bmatrix}
            r_2 \\ r_1
        \end{bmatrix}\right) \\ 
        \det I &= 1
\begin{definition}[Determinant Functions]
    Any function $f$ that satisfies the properties:
        \item $f\left(\begin{bmatrix}
            br_1 + cr_1^\prime \\ r_2 \\ \vdots \\ r_n
        \end{bmatrix}\right) = bf\left(\begin{bmatrix}
            r_1 \\ r_2 \\ \vdots \\ r_n
        \end{bmatrix}\right) + cf\left(\begin{bmatrix}
            r_1^\prime \\ r_2 \\ \vdots \\ r_n
        \end{bmatrix}\right)$ (Multilinearity in rows)

        \item $f\left(\begin{bmatrix}
            r_1 \\ r_2 \\ \vdots \\ r_i \\ \vdots \\ r_j \\ \vdots \\ r_n
        \end{bmatrix}\right) = -f\left(\begin{bmatrix}
            r_1 \\ r_2 \\ \vdots \\ r_j \\ \vdots \\ r_i \\ \vdots \\ r_n
        \end{bmatrix}\right)$ (Alternating property)

        \item $f(A) = (\det A )f(I)$
    \end{enumerate}
    is called a determinant function.
\end{definition}
\end{theorem}
\end{document}

### 2025-03-09 MSE160 Lecture Notes/main.tex
march 9

@@

>>>>

\paragraph{Vacancies} Vacancies are missing atoms in the lattice. They are created by thermal vibrations. They are used to inhibit the movement of dislocations.

@@

\section{Polymers} 
\paragraph{Polymer} Polymers could be britte or elastic (elastomers). They are made of long chains of monomers. Interestingly, polymers have necking points lower than its ultimate tensile strength.
\begin{center}
    \textit{``Why does polymers continue to stretch after necking?''}
\end{center}
\paragraph{Polymer Structure} Polymers are made of long chains of monomers. The chains are held together by weak van der Waals forces. The chains are entangled.
\\ (Example) Polyethylene are made of long chains of carbon atoms with two hydrogen atoms attached to each carbon atom.
\paragraph{Ans: (Chain-Oriented)} The chains are originally entangled. When the polymer is stretched, the chains are straightened to align with the load. More of the load is taken by the covalent bonds, which are stronger than the van der Waals forces. This serves as an important strengthening mechanism.
\paragraph{Note} In a polymer, the elastic response is from numerrous bond types.
\paragraph{Crylistallinity} Polymers cannot be 100\% crystalline. A polymer could be semi-crystalline, where the polymer has both crystalline and amorphous regions. Since the crystalline regions are stronger, increasing the crystallinity is a important strengthening mechanism.
    \item \textbf{Tmerpeature} Increasing the crtystallinity permits the polymer have higher service temperature. 
    \item \textbf{Chemical Resistance} Crystalline regions are more resistant to chemcial dissolution.
\paragraph{Different Mer Units} Different mer units have different properties. Listed below are some common mer units:
    \item \textbf{Polyethylene} (PE) - Made of long chains of carbon atoms with two hydrogen atoms attached to each carbon atom.
    \item \textbf{Polypropylene} (PP) - Similar to PE, but with a methyl group attached to the carbon atom.
    \item \textbf{Polyvinyl Chloride} (PVC) - Made of long chains of carbon atoms with a chlorine atom attached to each carbon atom. Chlorine are more electronegative than carbon, so the bond is polar and form stornger van der Waals forces.
    \item \textbf{Polystyrene} (PS) - Made of long chains of carbon atoms with a phenyl group attached to each carbon atom.
    \item \textbf{Polytetrafluoroethylene} (PTFE) - Made of long chains of carbon atoms with two fluorine atoms attached to each carbon atom. The florine is to protect the carbon backbone. Hoowever, it is mechanically weak as the dipole moment is low.
    \item \textbf{Polymethyl Methacrylate} (PMMA) - Made of long chains of carbon atoms with a methyl group and a methacrylate ($-\ch{OC(=O)}$) group attached to each carbon atom. It is opticall tranparnet the methacrylate group prevent crtystallinity, hence amorphous and no crystal boundaries.
\subsection{Viscoelasitcity and Thermal Properties}
\paragraph{Viscoelasticity} Polymers are viscoelastic. They have both viscous and elastic properties. The viscous properties are due to the entanglement of the chains. The elastic properties are due to the covalent bonds.
\paragraph{Time-Dependent Behavior} For a given stress/strain, the strain/stress will decrease with time. This is due to the viscous properties of the polymer.
\paragraph{Relaxation Modulus} The relaxation modulus is the modulus of the polymer as a function of time. It is given by:
    E(t) = \frac{\sigma(t)}{\epsilon_0}
The relaxation modulus is also relate to the temperature of the polymer. The relaxation modulus decreases with temperature.
\paragraph{Glassy Transition} The glassy transition is the temperature at which the polymer changes from a glassy state to a rubbery state. The glassy state is characterized by a high modulus and low strain. The rubbery state is characterized by a low modulus and high strain. The temperature is denoted as $T_g$.
This is due to the temperature overcoming the intermolecular forces of the amorphous reigions, but the crystalline regions are still intact as the van der Waals foce is stronger.
\paragraph{Melting} THe melting temperature is the temperature at which the polyme the intermolecular forces of the crystalline regions are overcome. The polymer then melts as chains slide past each other. 
\paragraph{Thermosat} Thermosat are polymers that do not melt. They are made of cross-linked chains or network polymers. The cross-links prevent the chains from sliding past each other. Elastomers are typically thermosets.
\subsection{Optical Properties}
\paragraph{PMMA} PMMA is a transparent polymer. It is used in optical applications. The transparency is due to the lack of \textbf{scattering events}.
\begin{definition}[Scatter Event]
    A scatter event is an event that causes light to be scattered. It is due to the difference in refractive index between the polymer and the air.
